Phase Delay Increases Repair Time. Not.

### 2015-02-18 phaseDelay.tex
Updates from ShareLaTeX

\documentclass{sig-alternative}
%\usepackage{multirow}
%\usepackage{color}
%% \usepackage{colortbl}
%% \usepackage{picture}
%% %\%usepackage{algorithm}
%% %\usepackage{algorithmicx}
%% %\usepackage{algpseudocode}
%% %\renewcommand{\algorithmicrequire}{\textbf{Input:}}
%% %\renewcommand{\algorithmicensure}{\textbf{Output:}}
%% \newcommand{\quart}[3]{\begin{picture}(100,6)%1
%% {\color{black}\put(#3,3){\circle*{4}}\put(#1,3){\line(1,0){#2}}}\end{picture}}

%% %% timm tricks
%% \newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
%% \newcommand{\ei}{\end{itemize}}
%% \newcommand{\be}{\begin{enumerate}}
%% \newcommand{\ee}{\end{enumerate}}
%% \newcommand{\tion}[1]{\S\ref{sect:#1}}
%% \newcommand{\fig}[1]{Figure~\ref{fig:#1}}
%% \newcommand{\eq}[1]{Equation~\ref{eq:#1}}

%% %% space saving measures

%% \usepackage[shortlabels]{enumitem} 
%% %\usepackage{times}

%% \usepackage{url}
%% \def\baselinestretch{1}

%% \setlist{nosep}
%%  \usepackage[font={small}]{caption, subfig}
%% \setlength{\abovecaptionskip}{1ex}
%%  \setlength{\belowcaptionskip}{1ex}

%%  \setlength{\floatsep}{1ex}
%%  \setlength{\textfloatsep}{1ex}
%% %\usepackage[compact,small]{titlesec}
%% \DeclareMathSizes{7}{7}{7}{7} 
%% \pagenumbering{arabic}
%% \setlength{\columnsep}{7mm}

@@

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{}
\numberofauthors{2}
\author{
\alignauthor
Tim Menzies, Carter Pape\\
       \affaddr{CS, NcState, USA}\\
       tim.menzies@gmail.com,\\carterpape@gmail.com
\alignauthor
Lucas Layman\\
       \affaddr{Fraunhofer Center, Exp. SE, USA}\\ 
       llayman@fc-md.umd.edu
\alignauthor
William Curtis, Forrest Schull\\
\affaddr{SEI, CMU, USA}
wrn,fjshull@sei.cmu.edu
}

\maketitle
\begin{abstract}

%RQ1: Does tuning affect learners' performance?
%RQ2: How to choose

\end{abstract}

% A category with the (minimum) three required fields
\vspace{1mm}
\noindent
{\bf Categories/Subject Descriptors:} 
D.2.8 [Software Engineering]: Product metrics;
I.2.6 [Artificial Intelligence]: Induction

\vspace{1mm}
\noindent
{\bf General Terms:} Experimentation, Algorithm}

\vspace{1mm}
\noindent
{\bf Keywords:} defect prediction, CART, random forests,
Fastmap,   bootstrap sampling, effect size, A12.

>>>>

\documentclass{sig-alternate}
\usepackage{multirow}
\usepackage{color}
\usepackage{colortbl}
\usepackage{picture}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

%timm tricks
\newcommand{\bi}{\begin{itemize}[leftmargin=0.4cm]}
\newcommand{\ei}{\end{itemize}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\tion}[1]{\S\ref{sect:#1}}
\newcommand{\fig}[1]{Figure~\ref{fig:#1}}
\newcommand{\eq}[1]{Equation~\ref{eq:#1}}

\usepackage[shortlabels]{enumitem} 
\usepackage{times}
\newcommand{\subparagraph}{}
\usepackage{url}
\def\baselinestretch{1}

\setlist{nosep}
 \usepackage[font={small}]{caption, subfig}
\setlength{\abovecaptionskip}{1ex}
 \setlength{\belowcaptionskip}{1ex}

 \setlength{\floatsep}{1ex}
 \setlength{\textfloatsep}{1ex}
\usepackage[compact,small]{titlesec}
\DeclareMathSizes{7}{7}{7}{7} 
\pagenumbering{arabic}
\setlength{\columnsep}{7mm}

@@

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Phase Delay Increases  Repair Time. Not.}
\numberofauthors{3}
\author{
\alignauthor
Tim Menzies, \\Carter Pape\\
       \affaddr{CS, NcState, USA}\\
       tim.menzies@gmail.com,\\carterpape@gmail.com
\alignauthor
William Curtis,\\ Forrest Schull\\
\affaddr{SEI, CMU, USA}
wrn,fjshull@sei.cmu.edu
\alignauthor
Lucas \\Layman\\
       \affaddr{Fraunhofer Center,  USA}\\ 
       llayman@fc-md.umd.edu
}

\maketitle
\begin{abstract}
This paper categorically rejects 
the myth that 
the longer a defect persists in a system, the harder
it is to remove that defect.  
This myth is very widely believed
and that the evidence for this myth dates back to certain
isolated studies dating from the 1970s. Recent evidence from
230 software projects from around the world shows that this
myth is completely false.

More important that our particular results, this paper
raises the methodological question of how a small number
of observations from the 1970s can become dogma for decades.
The obvious next question arising from this study is ``how
many other widely held beliefs in software engineering are
not supported by current data?''.
\end{abstract}

% A category with the (minimum) three required fields
\vspace{1mm}
\noindent
{\bf Categories/Subject Descriptors:} 
D.2.8 [Software Engineering]: Product metrics;

\vspace{1mm}
\noindent
{\bf Keywords:} defect prediction,
